Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-04 volunteer-clouds-ieee-ci-si.tex
Finishing intro to experiments

\begin{figure}[!t]
\centering
\includegraphics[width=12cm]{img/baseline-times.png}
\caption{Comparison of time to solution for the baseline system, using a {\tt
    node.js} client, for different population sizes. They only compare
runs in which solution has been found.}
\label{fig:baseline}
\end{figure}
First we establish the baseline performance by running the
evolutionary algorithm in a desktop client written using {\sf NodEO},
the node.js evolutionary algorithm library. This experiment tries to
find the solution to the 40-trap function with parameters $l=4, a=1,
b=2, z=3$, a population size equal 512, which was found in previous
experiments to be the correct one for finding the solution 95\% of the
time. The algorithm was run until the solution (a string with all
ones) was found or five millions evaluations had been performed. It
took around a minute, on average, that is $68.9694$ seconds, to
perform the fifty runs. In this experiment only 33, that is, 66\% were
successful. The experiments were repeated for population $p=1024$,
with success rate upgraded to 100\%. Results for these two experiments
are shown in Figure \ref{fig:baseline}.

>>>>

\begin{figure}[!t]
\centering
\includegraphics[width=12cm]{img/baseline-times.png}
\caption{Comparison of time to solution for the baseline system, using a {\tt
    node.js} client, for different population sizes. They only compaonre
runs in which solution has been found.}
\label{fig:baseline}
\end{figure}
First we establish the baseline performance by running the
evolutionary algorithm in a desktop client written using {\sf NodEO},
the node.js evolutionary algorithm library. This experiment tries to
find the solution to the 40-trap function with parameters $l=4, a=1,
b=2, z=3$, a population size equal 512, which was found in previous
experiments to be the correct one for finding the solution 95\% of the
time. The algorithm was run until the solution (a string with all
ones) was found or five millions evaluations had been performed. It
took around a minute, on average, that is $68.9694$ seconds, to
perform the fifty runs. In this experiment only 33, that is, 66\% were
successful. The experiments were repeated for population $p=1024$,
with success rate upgraded to 100\% and average duration $3.46
seconds$. Results for these two experiments 
are shown in Figure \ref{fig:baseline}.

These two experiments establish first a baseline result, which will
depend on the population. The volunteer computing experiments that we
will describe next do not and can not have the same conditions, but
the baseline is that if they eventually take longer than a basic
destktop, their interest will be purely academic. We will try and
prove next that that target performance can be achieved by carrying
out several experiments in different conditions.

\subsection{Volunteer evolutionary computation: first experiments and results}
